Preprocessing

### 2023-07-13 docs/presentation/preprocess.Rmd
viz: more word clouds

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
# library(showtext)
# font_add_google("Fira Sans", "Fira Sans")

analysis <- read_csv("analysis_hegs_rpr.csv", col_select = starts_with("Q"))
```

@@

@@

~~Per group?~~

```{r DRY wordcloud}
column_to_cloud <- function(
    col, threshold,
    my_palette = c(
      "#cdb4db",
      "#6d597a",
      "#b56576",
      "#e56b6f",
      "#eaac8b"
    )) {
  require(tidytext)
  word_counts <- analysis %>%
    drop_na(all_of(col)) %>%
    unnest_tokens("word", col) %>%
    anti_join(stop_words, by = "word") %>%
    count(word) %>%
    filter(n >= threshold)

@@

Question 10: Thinking about the reproduction(s) you attempted in the last 2 years, what made you decide to attempt the reproduction(s)?

Question 6: What is your understanding of the term "reproducibility" in the context of your own research?

Question 12a: If you were not able to submit all of the findings of your reproduction(s) for publication, why not?

Question 15: Please list any other factors that you believe contribute to a lack of reproducibility in research in your subfield.

Question 17a: Please list any benefits or important function of reproducibility in your subfield not mentioned above.

```{r word clouds}
clouds <- list()
clouds$q6 <- column_to_cloud("Q6", 6)
clouds$q10 <- column_to_cloud("Q10", 4)
clouds$q12a <- column_to_cloud("Q12a", 2)
clouds$q15 <- column_to_cloud("Q15", 4)
clouds$q17a <- column_to_cloud("Q17a", 2)
saveRDS(clouds, file = "clouds.rds")
```

>>>>

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
# library(showtext)
# font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
```

@@

Q19: demographics

Potentially split into professor - not professor

@@

Q6
Q10
Q12a
Q15
Q17a

Potentially per group, but only for Q6

```{r DRY wordcloud}
column_to_cloud <- function(
    col, nrows = 30,
    data = analysis,
    my_palette = c(
      "#cdb4db",
      "#6d597a",
      "#b56576",
      "#e56b6f",
      "#eaac8b"
    )) {
  require(tidytext)
  word_counts <- data %>%
    drop_na(all_of(col)) %>%
    unnest_tokens("word", col) %>%
    # https://bookdown.org/psonkin18/berkshire/tokenize.html#text-normalization---stemming-and-lemmatization
    # doesn't work - why is `reproduct` different from `reproduc`?
    # mutate(word = SnowballC::wordStem(word, language = "english")) %>%
    anti_join(stop_words, by = "word") %>%
    count(word) %>%
    arrange(desc(n)) %>%
    slice(1:nrows)

@@

```{r word clouds}
cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
saveRDS(clouds, file = "data/clouds.rds")
```

```{r q6 cloud}
subfields <- list("Human", "Methods", "Nature/society", "Physical")
types <- list("Quantitative", "Qualitative", "Mixed Methods")

clouds_q6_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q6", data = .)
) %>%
  set_names(subfields)

clouds_q6_q4 <- map(
  types, ~ analysis %>%
    filter(Q4 == .x) %>%
    column_to_cloud("Q6", data = .)
) %>%
  set_names(types)

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

## Likert charts
Q8

Q9 (maybe)

Q11
Q12

Q14

Q17

## Density plots
Include animations?

Q5 (maybe put with Q6's word cloud)

Q7 (many parts)

Q13 (percentages)

## Bar plot
Or something simple
Include animations

Q16

## Demographics
